Improving the portuguese hyphenation rules

### 2024-07-02 article/comparedresults.tex
fix #56

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

acuidade & a*cu-i*da*de \xmark & a*cu-i*da*de \xmark \\

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

aluimento & a*lu-i*men*to \xmark & a*lu-i*men*to \xmark \\

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

arrais & ar*ra-is \xmark & ar*ra-is \xmark \\

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

abegoaria & a*be*go*a*ri*a \cmark & a*be*go*a*ri-a \xmark \\
abiótica & a*bi-ó*ti*ca \xmark & a*bi*ó*ti*ca \cmark \\

@@

abiu & a*bi-u \xmark & a*bi*u \cmark \\

@@

abortício & a*bor*tí*ci.o \xmark & a*bor*tí*cio \cmark \\

@@

abruptamente & a.b-rup*ta*men*te \xmark & a.b-rup*ta*men*te \xmark \\

@@

absenteísta & ab*sen*te-ís*ta \xmark & ab*sen*te*ís*ta \cmark \\
absorvância & ab*sor*vân*ci.a \xmark & ab*sor*vân*cia \cmark \\
absorvência & ab*sor*vên*ci.a \xmark & ab*sor*vên*cia \cmark \\
abstêmio & abs*tê*mi.o \xmark & abs*tê*mio \cmark \\

@@

acácio & a*cá*ci.o \xmark & a*cá*cio \cmark \\

@@

acadêmia & a*ca*dê*mi.a \xmark & a*ca*dê*mia \cmark \\
acádio & a*cá*di.o \xmark & a*cá*dio \cmark \\

@@

acalmia & a*cal*mi*a \cmark & a*cal*mi-a \xmark \\

@@

acauã & a*cau-ã \xmark & a*cau*ã \cmark \\

@@

acelerômetro & a*ce*le-rô*me*tro \xmark & a*ce*le*rô*me*tro \cmark \\

@@

acidúria & a*ci*dú*ri.a \xmark & a*ci*dú*ria \cmark \\

@@

acroleína & a*cro*le-í*na \xmark & a*cro*le*í*na \cmark \\
acromatopsia & a*cro*ma*top*si*a \cmark & a*cro*ma*top*si-a \xmark \\

@@

acrotério & a*cro*té*ri.o \xmark & a*cro*té*rio \cmark \\

@@

@@

acusatório & a*cu*sa*tó*ri.o \xmark & a*cu*sa*tó*rio \cmark \\

@@

adenia & a*de*ni*a \cmark & a*de*ni-a \xmark \\
aderência & a*de*rên*ci.a \xmark & a*de*rên*cia \cmark \\

@@

adjacência & ad*ja*cên*ci.a \xmark & ad*ja*cên*cia \cmark \\

@@

adônis & a-dô*nis \xmark & a*dô*nis \cmark \\

@@

adstringência & ads*trin*gên*ci.a \xmark & ads*trin*gên*cia \cmark \\
adua & a*du*a \cmark & a*du-a \xmark \\
adulária & a*du*lá*ri.a \xmark & a*du*lá*ria \cmark \\

@@

adventícia & ad*ven*tí*ci.a \xmark & ad*ven*tí*cia \cmark \\

@@

advogacia & ad*vo*ga*ci*a \cmark & ad*vo*ga*ci-a \xmark \\

@@

aerofólio & a*e*ro*fó*li.o \xmark & a*e*ro*fó*lio \cmark \\

@@

aeromancia & a*e*ro*man*ci*a \cmark & a*e*ro*man*ci-a \xmark \\

@@

ágio & á*gi*o \cmark & á*gi-o \xmark \\

@@

agônico & a-gô*ni*co \xmark & a*gô*ni*co \cmark \\

@@

agroindústria & a*gro-in*dús*tri.a \xmark & a*gro*in*dús*tria \cmark \\

@@

agropecuária & a*gro*pe*cu-á*ri.a \xmark & a*gro*pe*cu*á*ria \cmark \\
agroquímica & a*gro-quí*mi*ca \xmark & a*gro*quí*mi*ca \cmark \\
agroquímico & a*gro-quí*mi*co \xmark & a*gro*quí*mi*co \cmark \\
aguaí & a*gua-í \xmark & a*gua*í \cmark \\

@@

ainsa & a-in*sa \xmark & a-in*sa \xmark \\

@@

aiquidô & ai*qui-dô \xmark & ai*qui*dô \cmark \\
ajuizado & a*ju-i*za*do \xmark & a*ju*i*za*do \cmark \\

@@

alagoa & a*la*go*a \cmark & a*la*go-a \xmark \\
alagoinha & a*la*go-i*nha \xmark & a*la*go*i*nha \cmark \\

@@

albuminúria & al*bu*mi*nú*ri.a \xmark & al*bu*mi*nú*ria \cmark \\

@@

alcaptonúria & al*cap*to*nú*ri.a \xmark & al*cap*to*nú*ria \cmark \\

@@

álea & á*le.a \xmark & á*lea \cmark \\

@@

alfandegário & al*fan*de*gá*ri.o \xmark & al*fan*de*gá*rio \cmark \\

@@

almóada & al*mó-a*da \xmark & al*mó-a*da \xmark \\

@@

aluá & a*lu-á \xmark & a*lu*á \cmark \\

@@

@@

amalteia & a*mal*tei*a \cmark & a*mal*tei-a \xmark \\

@@

amazia & a*ma*zi*a \cmark & a*ma*zi-a \xmark \\

@@

ambiência & am*bi*ên*ci.a \xmark & am*bi*ên*cia \cmark \\
ambivalência & am*bi*va*lên*ci.a \xmark & am*bi*va*lên*cia \cmark \\
ambliopia & am*bli*o*pi*a \cmark & am*bli*o*pi-a \xmark \\

@@

ambrósia & am*bró*si.a \xmark & am*bró*sia \cmark \\
ambulacrário & am*bu*la*crá*ri.o \xmark & am*bu*la*crá*rio \cmark \\

@@

amêijoa & a*mêi*jo.a \xmark & a*mêi*joa \cmark \\
amelia & a*me*li*a \cmark & a*me*li-a \xmark \\

@@

americanofilia & a*me*ri*ca*no*fi*li*a \cmark & a*me*ri*ca*no*fi*li-a \xmark \\
americanofobia & a*me*ri*ca*no*fo*bi*a \cmark & a*me*ri*ca*no*fo*bi-a \xmark \\

@@

amigdalectomia & a*mig*da*lec*to*mi*a \cmark & a*mig*da*lec*to*mi-a \xmark \\

@@

amnesia & am*ne*si*a \cmark & am*ne*si-a \xmark \\
âmnio & âm*ni.o \xmark & âm*nio \cmark \\
amônia & a-mô*ni.a \xmark & a*mô*nia \cmark \\

@@

anastácio & a*nas*tá*ci.o \xmark & a*nas*tá*cio \cmark \\
anatólio & a*na*tó*li.o \xmark & a*na*tó*lio \cmark \\

@@

anauê & a*nau-ê \xmark & a*nau*ê \cmark \\

@@

androfilia & an*dro*fi*li*a \cmark & an*dro*fi*li-a \xmark \\

@@

anedotário & a*ne*do*tá*ri.o \xmark & a*ne*do*tá*rio \cmark \\

@@

anencefalia & a*nen*ce*fa*li*a \cmark & a*nen*ce*fa*li-a \xmark \\

@@

anfião & an*fi-ão \xmark & an*fi*ão \cmark \\

@@

anfibólio & an*fi*bó*li.o \xmark & an*fi*bó*lio \cmark \\

@@

anfictião & an*fic*ti-ão \xmark & an*fic*ti*ão \cmark \\
anfictionia & an*fic*ti*o*ni*a \cmark & an*fic*ti*o*ni-a \xmark \\

@@

angelologia & an*ge*lo*lo*gi*a \cmark & an*ge*lo*lo*gi-a \xmark \\
angiografia & an*gi*o*gra*fi*a \cmark & an*gi*o*gra*fi-a \xmark \\

@@

angioscopia & an*gi*os*co*pi*a \cmark & an*gi*os*co*pi-a \xmark \\
anglofilia & an*glo*fi*li*a \cmark & an*glo*fi*li-a \xmark \\
anglofonia & an*glo*fo*ni*a \cmark & an*glo*fo*ni-a \xmark \\

@@

anião & a*ni-ão \xmark & a*ni*ão \cmark \\
aniridia & a*ni*ri*di*a \cmark & a*ni*ri*di-a \xmark \\

@@

anômalo & a-nô*ma*lo \xmark & a*nô*ma*lo \cmark \\

@@

ânsia & ân*si.a \xmark & ân*sia \cmark \\

@@

anterídio & an*te*rí*di.o \xmark & an*te*rí*dio \cmark \\
antestreia & an*tes*trei*a \cmark & an*tes*trei-a \xmark \\

@@

antiaéreo & an*ti*a-é*re.o \xmark & an*ti*a*é*reo \cmark \\

@@

antidemocracia & an*ti*de*mo*cra*ci*a \cmark & an*ti*de*mo*cra*ci-a \xmark \\
antiético & an*ti-é*ti*co \xmark & an*ti*é*ti*co \cmark \\
antifonário & an*ti*fo*ná*ri.o \xmark & an*ti*fo*ná*rio \cmark \\
antimatéria & an*ti*ma*té*ri.a \xmark & an*ti*ma*té*ria \cmark \\
antimônio & an*ti-mô*ni.o \xmark & an*ti*mô*nio \cmark \\

@@

antinômico & an*ti-nô*mi*co \xmark & an*ti*nô*mi*co \cmark \\

@@

antipoluição & an*ti*po*lu-i*ção \xmark & an*ti*po*lu*i*ção \cmark \\

@@

antúrio & an*tú*ri.o \xmark & an*tú*rio \cmark \\

@@

anúria & a*nú*ri.a \xmark & a*nú*ria \cmark \\

@@

apartidário & a*par*ti*dá*ri.o \xmark & a*par*ti*dá*rio \cmark \\

@@

aperiódico & a*pe*ri-ó*di*co \xmark & a*pe*ri*ó*di*co \cmark \\

@@

apomixia & a*po*mi*xi*a \cmark & a*po*mi*xi-a \xmark \\

@@

apoteótico & a*po*te-ó*ti*co \xmark & a*po*te*ó*ti*co \cmark \\

@@

aquariofilia & a*qua*ri*o*fi*li*a \cmark & a*qua*ri*o*fi*li-a \xmark \\

@@

aquênio & a-quê*ni.o \xmark & a*quê*nio \cmark \\

@@

aracnídeo & a*rac*ní*de.o \xmark & a*rac*ní*deo \cmark \\

@@

arapuá & a*ra*pu-á \xmark & a*ra*pu*á \cmark \\

@@

araúna & a*ra-ú*na \xmark & a*ra*ú*na \cmark \\

@@

arcádia & ar*cá*di.a \xmark & ar*cá*dia \cmark \\

@@

arcaria & ar*ca*ri*a \cmark & ar*ca*ri-a \xmark \\

@@

areão & a*re-ão \xmark & a*re*ão \cmark \\

@@

areópago & a*re-ó*pa*go \xmark & a*re*ó*pa*go \cmark \\

@@

argônio & ar-gô*ni.o \xmark & ar*gô*nio \cmark \\

@@

ária & á*ri.a \xmark & á*ria \cmark \\

@@

armênio & ar*mê*ni.o \xmark & ar*mê*nio \cmark \\

@@

arquegônio & ar*que-gô*ni.o \xmark & ar*que*gô*nio \cmark \\

@@

arquiconfraria & ar*qui*con*fra*ri*a \cmark & ar*qui*con*fra*ri-a \xmark \\

@@

arquimilionário & ar*qui*mi*li*o*ná*ri.o \xmark & ar*qui*mi*li*o*ná*rio \cmark \\

@@

arraia & ar*rai*a \cmark & ar*rai-a \xmark \\
arredio & ar*re*di*o \cmark & ar*re*di-o \xmark \\

@@

arrogância & ar*ro*gân*ci.a \xmark & ar*ro*gân*cia \cmark \\

@@

arroteia & ar*ro*tei*a \cmark & ar*ro*tei-a \xmark \\

@@

arsênio & ar*sê*ni.o \xmark & ar*sê*nio \cmark \\

@@

artéria & ar*té*ri.a \xmark & ar*té*ria \cmark \\
arteriografia & ar*te*ri*o*gra*fi*a \cmark & ar*te*ri*o*gra*fi-a \xmark \\
arteríola & ar*te*rí-o*la \xmark & ar*te*rí*o*la \cmark \\

@@

aruá & a*ru-á \xmark & a*ru*á \cmark \\

@@

assembleia & as*sem*blei*a \cmark & as*sem*blei-a \xmark \\

@@

assincronia & as*sin*cro*ni*a \cmark & as*sin*cro*ni-a \xmark \\
assiriologia & as*si*ri*o*lo*gi*a \cmark & as*si*ri*o*lo*gi-a \xmark \\
assiriólogo & as*si*ri-ó*lo*go \xmark & as*si*ri*ó*lo*go \cmark \\

@@

assobio & as*so*bi*o \cmark & as*so*bi-o \xmark \\

@@

astéria & as*té*ri.a \xmark & as*té*ria \cmark \\
astreia & as*trei*a \cmark & as*trei-a \xmark \\
astrobiologia & as*tro*bi*o*lo*gi*a \cmark & as*tro*bi*o*lo*gi-a \xmark \\
astrofotografia & as*tro*fo*to*gra*fi*a \cmark & as*tro*fo*to*gra*fi-a \xmark \\

@@

astrometria & as*tro*me*tri*a \cmark & as*tro*me*tri-a \xmark \\

@@

astroquímica & as*tro-quí*mi*ca \xmark & as*tro*quí*mi*ca \cmark \\

@@

ataxia & a*ta*xi*a \cmark & a*ta*xi-a \xmark \\

@@

atônito & a-tô*ni*to \xmark & a*tô*ni*to \cmark \\
atopia & a*to*pi*a \cmark & a*to*pi-a \xmark \\

@@

atuário & a*tu-á*ri.o \xmark & a*tu*á*rio \cmark \\
audácia & au*dá*ci.a \xmark & au*dá*cia \cmark \\

@@

audiometria & au*di*o*me*tri*a \cmark & au*di*o*me*tri-a \xmark \\

@@

auê & au-ê \xmark & au*ê \cmark \\

@@

aurélia & au*ré*li.a \xmark & au*ré*lia \cmark \\

@@

autobiógrafo & au*to*bi-ó*gra*fo \xmark & au*to*bi*ó*gra*fo \cmark \\
autocomplacência & au*to*com*pla*cên*ci.a \xmark & au*to*com*pla*cên*cia \cmark \\
autoconsciência & au*to*cons*ci*ên*ci.a \xmark & au*to*cons*ci*ên*cia \cmark \\

@@

autodestruição & au*to*des*tru-i*ção \xmark & au*to*des*tru*i*ção \cmark \\
autodomínio & au*to*do*mí*ni.o \xmark & au*to*do*mí*nio \cmark \\

@@

autogamia & au*to*ga*mi*a \cmark & au*to*ga*mi-a \xmark \\
autogestionário & au*to*ges*ti*o*ná*ri.o \xmark & au*to*ges*ti*o*ná*rio \cmark \\

@@

autoimunidade & au*to-i*mu*ni*da*de \xmark & au*to*i*mu*ni*da*de \cmark \\

@@

autonômico & au*to-nô*mi*co \xmark & au*to*nô*mi*co \cmark \\

@@

averroísmo & a*ver*ro-ís*mo \xmark & a*ver*ro*ís*mo \cmark \\
avessia & a*ves*si*a \cmark & a*ves*si-a \xmark \\

@@

avio & a*vi*o \cmark & a*vi-o \xmark \\

@@

azagaia & a*za*gai*a \cmark & a*za*gai-a \xmark \\

@@

azaleia & a*za*lei*a \cmark & a*za*lei-a \xmark \\

@@

azotemia & a*zo*te*mi*a \cmark & a*zo*te*mi-a \xmark \\

@@

babilônico & ba*bi-lô*ni*co \xmark & ba*bi*lô*ni*co \cmark \\

@@

bacterioscopia & bac*te*ri*os*co*pi*a \cmark & bac*te*ri*os*co*pi-a \xmark \\

@@

bailio & bai*li*o \cmark & bai*li-o \xmark \\

@@

balbuciência & bal*bu*ci*ên*ci*a \cmark & bal*bu*ci*ên*ci-a \xmark \\

@@

baleárico & ba*le-á*ri*co \xmark & ba*le*á*ri*co \cmark \\

@@

baleio & ba*lei*o \cmark & ba*lei-o \xmark \\
balio & ba*li*o \cmark & ba*li-o \xmark \\

@@

bancaria & ban*ca*ri*a \cmark & ban*ca*ri-a \xmark \\

@@

banjoísta & ban*jo-ís*ta \xmark & ban*jo*ís*ta \cmark \\

@@

baraúna & ba*ra-ú*na \xmark & ba*ra*ú*na \cmark \\
barbaria & bar*ba*ri*a \cmark & bar*ba*ri-a \xmark \\

@@

barômetro & ba-rô*me*tro \xmark & ba*rô*me*tro \cmark \\
baronia & ba*ro*ni*a \cmark & ba*ro*ni-a \xmark \\

@@

batistério & ba*tis*té*ri.o \xmark & ba*tis*té*rio \cmark \\

@@

beduíno & be*du-í*no \xmark & be*du*í*no \cmark \\
behaviorismo & be-ha*vi*o*ris*mo \xmark & be-ha*vi*o*ris*mo \xmark \\
beligerância & be*li*ge*rân*ci.a \xmark & be*li*ge*rân*cia \cmark \\

@@

benemerência & be*ne*me*rên*ci.a \xmark & be*ne*me*rên*cia \cmark \\

@@

benfeitoria & ben*fei*to*ri*a \cmark & ben*fei*to*ri-a \xmark \\

@@

benzocaína & ben*zo*ca-í*na \xmark & ben*zo*ca*í*na \cmark \\

@@

berquélio & ber-qué*li.o \xmark & ber*qué*lio \cmark \\

@@

bestiário & bes*ti-á*ri.o \xmark & bes*ti*á*rio \cmark \\

@@

bíblia & bí*bli.a \xmark & bí*blia \cmark \\

@@

bibliofobia & bi*bli*o*fo*bi*a \cmark & bi*bli*o*fo*bi-a \xmark \\

@@

bibliógrafo & bi*bli-ó*gra*fo \xmark & bi*bli*ó*gra*fo \cmark \\

@@

bibliotecário & bi*bli*o*te*cá*ri.o \xmark & bi*bli*o*te*cá*rio \cmark \\

@@

bicuíba & bi*cu-í*ba \xmark & bi*cu*í*ba \cmark \\
biênio & bi*ê*ni.o \xmark & bi*ê*nio \cmark \\

@@

bilbaíno & bil*ba-í*no \xmark & bil*ba*í*no \cmark \\

@@

bilião & bi*li-ão \xmark & bi*li*ão \cmark \\
bilionário & bi*li*o*ná*ri.o \xmark & bi*li*o*ná*rio \cmark \\

@@

binômio & bi-nô*mi.o \xmark & bi*nô*mio \cmark \\
biociência & bi*o*ci*ên*ci.a \xmark & bi*o*ci*ên*cia \cmark \\

@@

biofilia & bi*o*fi*li*a \cmark & bi*o*fi*li-a \xmark \\

@@

bioluminescência & bi*o*lu*mi*nes*cên*ci.a \xmark & bi*o*lu*mi*nes*cên*cia \cmark \\

@@

bioquímico & bi*o-quí*mi*co \xmark & bi*o*quí*mi*co \cmark \\

@@

biótopo & bi-ó*to*po \xmark & bi*ó*to*po \cmark \\
bipartidário & bi*par*ti*dá*ri.o \xmark & bi*par*ti*dá*rio \cmark \\

@@

bissemanário & bis*se*ma*ná*ri.o \xmark & bis*se*ma*ná*rio \cmark \\
biunívoco & bi-u*ní*vo*co \xmark & bi*u*ní*vo*co \cmark \\
bizâncio & bi*zân*ci.o \xmark & bi*zân*cio \cmark \\

@@

blasfêmia & blas*fê*mi.a \xmark & blas*fê*mia \cmark \\
blastômero & blas-tô*me*ro \xmark & blas*tô*me*ro \cmark \\

@@

boataria & bo*a*ta*ri*a \cmark & bo*a*ta*ri-a \xmark \\

@@

bócio & bó*ci.o \xmark & bó*cio \cmark \\
boé & bo-é \xmark & bo*é \cmark \\
boemia & bo*e*mi*a \cmark & bo*e*mi-a \xmark \\
bôer & bô-er \xmark & bô-er \xmark \\
boia & boi*a \cmark & boi-a \xmark \\

@@

borderô & bor*de-rô \xmark & bor*de*rô \cmark \\

@@

bosníaco & bos*ní-a*co \xmark & bos*ní*a*co \cmark \\

@@

brânquia & brân*qui.a \xmark & brân*quia \cmark \\
braquicefalia & bra*qui*ce*fa*li*a \cmark & bra*qui*ce*fa*li-a \xmark \\
braquidactilia & bra*qui*dac*ti*li*a \cmark & bra*qui*dac*ti*li-a \xmark \\
braquiópode & bra*qui-ó*po*de \xmark & bra*qui*ó*po*de \cmark \\
brasiguaio & bra*si*guai*o \cmark & bra*si*guai-o \xmark \\

@@

braúna & bra-ú*na \xmark & bra*ú*na \cmark \\

@@

broncoscopia & bron*cos*co*pi*a \cmark & bron*cos*co*pi-a \xmark \\

@@

bucelário & bu*ce*lá*ri.o \xmark & bu*ce*lá*rio \cmark \\

@@

bugia & bu*gi*a \cmark & bu*gi-a \xmark \\

@@

bútio & bú*ti.o \xmark & bú*tio \cmark \\

@@

cabeceio & ca*be*cei*o \cmark & ca*be*cei-o \xmark \\
cabrião & ca*bri-ão \xmark & ca*bri*ão \cmark \\
cabriúva & ca*bri-ú*va \xmark & ca*bri*ú*va \cmark \\

@@

cacauicultura & ca*cau-i*cul*tu*ra \xmark & ca*cau*i*cul*tu*ra \cmark \\

@@

cactácea & cac*tá*ce.a \xmark & cac*tá*cea \cmark \\

@@

cádmio & cád*mi.o \xmark & cád*mio \cmark \\

@@

caimento & ca-i*men*to \xmark & ca-i*men*to \xmark \\
caingangue & ca-in*gan*gue \xmark & ca-in*gan*gue \xmark \\

@@

caixilharia & cai*xi*lha*ri*a \cmark & cai*xi*lha*ri-a \xmark \\
caixotaria & cai*xo*ta*ri*a \cmark & cai*xo*ta*ri-a \xmark \\

@@

calcâneo & cal*câ*ne.o \xmark & cal*câ*neo \cmark \\

@@

calcedônia & cal*ce-dô*ni.a \xmark & cal*ce*dô*nia \cmark \\
calcemia & cal*ce*mi*a \cmark & cal*ce*mi-a \xmark \\

@@

caldário & cal*dá*ri.o \xmark & cal*dá*rio \cmark \\
caldeiraria & cal*dei*ra*ri*a \cmark & cal*dei*ra*ri-a \xmark \\

@@

califasia & ca*li*fa*si*a \cmark & ca*li*fa*si-a \xmark \\
califórnia & ca*li*fór*ni*a \cmark & ca*li*fór*ni-a \xmark \\
califórnio & ca*li*fór*ni.o \xmark & ca*li*fór*nio \cmark \\

@@

calistenia & ca*lis*te*ni*a \cmark & ca*lis*te*ni-a \xmark \\

@@

calúnia & ca*lú*ni.a \xmark & ca*lú*nia \cmark \\

@@

calvície & cal*ví*ci.e \xmark & cal*ví*cie \cmark \\

@@

camarário & ca*ma*rá*ri.o \xmark & ca*ma*rá*rio \cmark \\

@@

cambaleio & cam*ba*lei*o \cmark & cam*ba*lei-o \xmark \\

@@

canário & ca*ná*ri.o \xmark & ca*ná*rio \cmark \\
cancelário & can*ce*lá*ri.o \xmark & can*ce*lá*rio \cmark \\

@@

canônico & ca-nô*ni*co \xmark & ca*nô*ni*co \cmark \\

@@

capacitância & ca*pa*ci*tân*ci.a \xmark & ca*pa*ci*tân*cia \cmark \\

@@

capeia & ca*pei*a \cmark & ca*pei-a \xmark \\

@@

capnomancia & cap*no*man*ci*a \cmark & cap*no*man*ci-a \xmark \\

@@

capricórnio & ca*pri*cór*ni.o \xmark & ca*pri*cór*nio \cmark \\

@@

carabídeo & ca*ra*bí*de.o \xmark & ca*ra*bí*deo \cmark \\
caracterologia & ca*rac*te*ro*lo*gi*a \cmark & ca*rac*te*ro*lo*gi-a \xmark \\

@@

cárdia & cár*di.a \xmark & cár*dia \cmark \\

@@

cardinalício & car*di*na*lí*ci.o \xmark & car*di*na*lí*cio \cmark \\

@@

cardiomiopatia & car*di*o*mi*o*pa*ti*a \cmark & car*di*o*mi*o*pa*ti-a \xmark \\
cardiopatia & car*di*o*pa*ti*a \cmark & car*di*o*pa*ti-a \xmark \\
cardiorrespiratório & car*di*or*res*pi*ra*tó*ri.o \xmark & car*di*or*res*pi*ra*tó*rio \cmark \\
carélio & ca*ré*li.o \xmark & ca*ré*lio \cmark \\

@@

cariogamia & ca*ri*o*ga*mi*a \cmark & ca*ri*o*ga*mi-a \xmark \\

@@

carnaíba & car*na-í*ba \xmark & car*na*í*ba \cmark \\

@@

carnaubal & car*na-u*bal \xmark & car*na-u*bal \xmark \\
caroá & ca*ro-á \xmark & ca*ro*á \cmark \\

@@

carroçaria & car*ro*ça*ri*a \cmark & car*ro*ça*ri-a \xmark \\

@@

cartorário & car*to*rá*ri.o \xmark & car*to*rá*rio \cmark \\

@@

cartulário & car*tu*lá*ri.o \xmark & car*tu*lá*rio \cmark \\

@@

castelania & cas*te*la*ni*a \cmark & cas*te*la*ni-a \xmark \\

@@

cataplexia & ca*ta*ple*xi*a \cmark & ca*ta*ple*xi-a \xmark \\

@@

catatônico & ca*ta-tô*ni*co \xmark & ca*ta*tô*ni*co \cmark \\
catenária & ca*te*ná*ri.a \xmark & ca*te*ná*ria \cmark \\

@@

catexia & ca*te*xi*a \cmark & ca*te*xi-a \xmark \\

@@

cedência & ce*dên*ci.a \xmark & ce*dên*cia \cmark \\

@@

celíaco & ce*lí-a*co \xmark & ce*lí*a*co \cmark \\
celibatário & ce*li*ba*tá*ri.o \xmark & ce*li*ba*tá*rio \cmark \\

@@

censório & cen*só*ri.o \xmark & cen*só*rio \cmark \\

@@

cerambicídeo & ce*ram*bi*cí*de.o \xmark & ce*ram*bi*cí*deo \cmark \\
ceratoplastia & ce*ra*to*plas*ti*a \cmark & ce*ra*to*plas*ti-a \xmark \\
cercania & cer*ca*ni*a \cmark & cer*ca*ni-a \xmark \\

@@

cerimônia & ce*ri-mô*ni.a \xmark & ce*ri*mô*nia \cmark \\

@@

cervídeo & cer*ví*de.o \xmark & cer*ví*deo \cmark \\

@@

cesáreo & ce*sá*re.o \xmark & ce*sá*reo \cmark \\

@@

cestaria & ces*ta*ri*a \cmark & ces*ta*ri-a \xmark \\

@@

champô & cham-pô \xmark & cham*pô \cmark \\

@@

chapelaria & cha*pe*la*ri*a \cmark & cha*pe*la*ri-a \xmark \\
charcutaria & char*cu*ta*ri*a \cmark & char*cu*ta*ri-a \xmark \\

@@

chororô & cho*ro-rô \xmark & cho*ro*rô \cmark \\
chuleio & chu*lei*o \cmark & chu*lei-o \xmark \\

@@

ciática & ci-á*ti*ca \xmark & ci*á*ti*ca \cmark \\

@@

ciberespaço & ci*be.r-es*pa*ço \xmark & ci*be.r-es*pa*ço \xmark \\
cibório & ci*bó*ri.o \xmark & ci*bó*rio \cmark \\
cicio & ci*ci*o \cmark & ci*ci-o \xmark \\
ciclídeo & ci*clí*de.o \xmark & ci*clí*deo \cmark \\

@@

cicloviário & ci*clo*vi-á*ri.o \xmark & ci*clo*vi*á*rio \cmark \\

@@

cientologia & ci*en*to*lo*gi*a \cmark & ci*en*to*lo*gi-a \xmark \\
cilício & ci*lí*ci.o \xmark & ci*lí*cio \cmark \\

@@

cinérea & ci*né*re.a \xmark & ci*né*rea \cmark \\

@@

cinesiologia & ci*ne*si*o*lo*gi*a \cmark & ci*ne*si*o*lo*gi-a \xmark \\
cinesioterapia & ci*ne*si*o*te*ra*pi*a \cmark & ci*ne*si*o*te*ra*pi-a \xmark \\

@@

ciprinídeo & ci*pri*ní*de.o \xmark & ci*pri*ní*deo \cmark \\
circulatório & cir*cu*la*tó*ri.o \xmark & cir*cu*la*tó*rio \cmark \\

@@

cistoscópio & cis*tos*có*pi.o \xmark & cis*tos*có*pio \cmark \\

@@

citopatologia & ci*to*pa*to*lo*gi*a \cmark & ci*to*pa*to*lo*gi-a \xmark \\

@@

clamídia & cla*mí*di.a \xmark & cla*mí*dia \cmark \\

@@

climatério & cli*ma*té*ri.o \xmark & cli*ma*té*rio \cmark \\

@@

clípeo & clí*pe.o \xmark & clí*peo \cmark \\

@@

coalescência & co*a*les*cên*ci.a \xmark & co*a*les*cên*cia \cmark \\
coautoria & co*au*to*ri*a \cmark & co*au*to*ri-a \xmark \\

@@

cóclea & có*cle.a \xmark & có*clea \cmark \\

@@

coimbrão & co-im*brão \xmark & co*im*brão \cmark \\

@@

coirmão & co-ir*mão \xmark & co-ir*mão \xmark \\

@@

coletânea & co*le*tâ*ne.a \xmark & co*le*tâ*nea \cmark \\
coletoria & co*le*to*ri*a \cmark & co*le*to*ri-a \xmark \\
colírio & co*lí*ri.o \xmark & co*lí*rio \cmark \\

@@

colódio & co*ló*di.o \xmark & co*ló*dio \cmark \\

@@

colônia & co-lô*ni.a \xmark & co*lô*nia \cmark \\

@@

colorimetria & co*lo*ri*me*tri*a \cmark & co*lo*ri*me*tri-a \xmark \\
colostomia & co*los*to*mi*a \cmark & co*los*to*mi-a \xmark \\
colposcopia & col*pos*co*pi*a \cmark & col*pos*co*pi-a \xmark \\
colposcópio & col*pos*có*pi.o \xmark & col*pos*có*pio \cmark \\
columbário & co*lum*bá*ri.o \xmark & co*lum*bá*rio \cmark \\
colúmbio & co*lúm*bi.o \xmark & co*lúm*bio \cmark \\

@@

colutório & co*lu*tó*ri.o \xmark & co*lu*tó*rio \cmark \\
comandância & co*man*dân*ci.a \xmark & co*man*dân*cia \cmark \\

@@

comedia & co*me*di*a \cmark & co*me*di-a \xmark \\

@@

comedoria & co*me*do*ri*a \cmark & co*me*do*ri-a \xmark \\
comendatário & co*men*da*tá*ri.o \xmark & co*men*da*tá*rio \cmark \\

@@

cometário & co*me*tá*ri.o \xmark & co*me*tá*rio \cmark \\

@@

compadrio & com*pa*dri*o \cmark & com*pa*dri-o \xmark \\

@@

comparência & com*pa*rên*ci.a \xmark & com*pa*rên*cia \cmark \\

@@

compilatório & com*pi*la*tó*ri.o \xmark & com*pi*la*tó*rio \cmark \\

@@

comunitário & co*mu*ni*tá*ri.o \xmark & co*mu*ni*tá*rio \cmark \\
concelhio & con*ce*lhi*o \cmark & con*ce*lhi-o \xmark \\
concessionária & con*ces*si*o*ná*ri.a \xmark & con*ces*si*o*ná*ria \cmark \\
concessionário & con*ces*si*o*ná*ri.o \xmark & con*ces*si*o*ná*rio \cmark \\

@@

conciliatório & con*ci*li*a*tó*ri.o \xmark & con*ci*li*a*tó*rio \cmark \\

@@

concomitância & con*co*mi*tân*ci.a \xmark & con*co*mi*tân*cia \cmark \\

@@

concordatário & con*cor*da*tá*ri.o \xmark & con*cor*da*tá*rio \cmark \\

@@

condômino & con-dô*mi*no \xmark & con*dô*mi*no \cmark \\
conduíte & con*du-í*te \xmark & con*du*í*te \cmark \\
condutância & con*du*tân*ci.a \xmark & con*du*tân*cia \cmark \\

@@

confirmatório & con*fir*ma*tó*ri.o \xmark & con*fir*ma*tó*rio \cmark \\

@@

côngio & côn*gi.o \xmark & côn*gio \cmark \\

@@

conivência & co*ni*vên*ci.a \xmark & co*ni*vên*cia \cmark \\

@@

consócio & con*só*ci.o \xmark & con*só*cio \cmark \\

@@

conspiratório & cons*pi*ra*tó*ri.o \xmark & cons*pi*ra*tó*rio \cmark \\

@@

contadoria & con*ta*do*ri*a \cmark & con*ta*do*ri-a \xmark \\

@@

conterrâneo & con*ter*râ*ne.o \xmark & con*ter*râ*neo \cmark \\
conteudista & con*te-u*dis*ta \xmark & con*te-u*dis*ta \xmark \\

@@

continuidade & con*ti*nu-i*da*de \xmark & con*ti*nu*i*da*de \cmark \\
continuísta & con*ti*nu-ís*ta \xmark & con*ti*nu*ís*ta \cmark \\

@@

contrabateria & con*tra*ba*te*ri*a \cmark & con*tra*ba*te*ri-a \xmark \\
contraditória & con*tra*di*tó*ri.a \xmark & con*tra*di*tó*ria \cmark \\

@@

contradomínio & con*tra*do*mí*ni.o \xmark & con*tra*do*mí*nio \cmark \\

@@

contraindicação & con*tra-in*di*ca*ção \xmark & con*tra*in*di*ca*ção \cmark \\

@@

contrastaria & con*tras*ta*ri*a \cmark & con*tras*ta*ri-a \xmark \\

@@

convocatória & con*vo*ca*tó*ri.a \xmark & con*vo*ca*tó*ria \cmark \\
convocatório & con*vo*ca*tó*ri.o \xmark & con*vo*ca*tó*rio \cmark \\
